\subsubsection{Backend Development}

The following tasks are implemented exclusively in the application 
backend logic.

\textbf{BD1. RESTful API Backend Logic Implementation}

Develop a RESTful API to manage backend responsibilities invoked by 
frontend requests.

\textbf{BD2. Azure SQL Database Integration}

Integrate Azure SQL Database with Entity Framework to enable create, 
read, update, and delete (CRUD) operations on the application's data. 
Relevant information is stored in SQL database for data manipulation and retrieval.

\textbf{BD3. Azure Blob Storage Integration}

Integrate Azure Blob Storage to save original expense files.

\textbf{BD4. Microsoft Document Intelligence AI Model Integration}

Integrate an AI model to automate the expense data extraction.

\textbf{BD5. Automated AI-driven Data Extraction Pipeline}

Integrate Event Grid and Service Bus into the expense upload pipeline, 
and implement a mechanized data extraction workflow. When a new receipt 
is uploaded and saved to Blob Storage and SQL Database, Azure Event Grid 
detects the event and routes it to Service Bus. This triggers automated 
submission to the AI model for processing, while preventing bottlenecks during 
multiple simultaneous uploads.

\newpage
\textbf{BD6. Azure SignalR Real-time Notification Service Integration}

Integrate SignalR into the backend logic, enabling the backend to notify the 
frontend whenever the AI model processes a receipt. Once the expense extraction 
has succeeded or failed, users are notified immediately, enabling real-time UI 
updates without requiring a manual page refresh.


\textbf{BD7. Microsoft Entra ID User Authentication Integration}

Integrate Microsoft Entra ID into the backend logic to handle employee 
authentication through the company email account.

