\subsubsection{Frontend and Backend Development}

Since this is a full-stack web application, the implementation 
encompasses both frontend and backend components. The frontend primarily 
handles the user interface (UI) and user experience (UX), encompassing 
all visual elements and user interactions of the application. The 
backend focuses on the core business logic, it handles more complex 
operations that are hidden in the frontend part and interacts with 
external services. The backend is implemented as a RESTful API that 
is called by the frontend when required.

\textbf{FBD1. Expense Uploads}

Provide a visual interface in the frontend for users to drag-and-drop 
or upload receipts. The backend will later handle database updates to 
register the new ticket and make it accessible on future logins.

\textbf{FBD2. Uploaded Expenses Real-time Dashboard}

Call the backend API from the frontend app for receiving all the previous 
uploaded receipts of the corresponding authenticated user. The backend 
is accountable for retrieving this information properly. Within this 
dashboard the current status of the expense is displayed, the possible 
statuses are:

\begin{itemize}[leftmargin=0.5cm,label={}]
    \item \textbf{Processing}

    \item The expense is still being processed by the AI model.

    \item \textbf{Pending Review}

    \item The AI model has successfully analyzed the expense, the uploader can 
    now review it.

    \newpage

    \item \textbf{Completed}

    \item The user has reviewed and completed all required information. The expense 
    is ready for being included in a new or existing report.

    \item \textbf{Failed} 

    \item The AI couldn't extract data from the receipt (either due to 
    unavailability or unrecognized format).

\end{itemize}

\textbf{FBD3. AI-Extracted Expense Data Review and Correction}

Let employees review AI-processed expenses and fill in the missing 
required information in the frontend UI. Once the user wants to save 
the new expense information, the backend will then update the 
database with the corrected data.

\textbf{FBD4. Uploaded Expenses Deletion}

Allow employees to delete any uploaded receipt, regardless of its 
current status. The frontend provides visual tools to delete one or 
multiple expenses. After the user confirms the deletion, the backend 
marks them as deleted in the database.

\textbf{FBD5. Expense Reports View, Creation, Edit, Submission, and Deletion}

Allow employees to create reports from uploaded, AI-processed, and 
reviewed expenses. They can edit the report details, 
submit for approval, or delete unsubmitted reports using the 
frontend UI. The backend updates the database status based on 
user actions.


\textbf{FBD6. Company Email User Authentication}

Grant employees login access using their company email account through the frontend login page.
The backend, which is integrated with Microsoft Entra ID,  verifies 
the user access. On first login, the backend creates a new user profile; on 
return visits, it retrieves the user's relevant data (e.g. previous uploaded expenses).

\textbf{FBD7.  Role-based User Access}

Assign the corresponding role to the logged-in user, either 
regular employee or administrator. Administrators have 
additional features unavailable to regular employees. 

When a user logs into the frontend app, the backend processes the user 
information to assign the appropriate role, enabling the frontend to 
display only the functionalities specific to that role.


\textbf{FBD8. Submitted Report Approval and Rejection}

Enable administrative users to view the reports submitted by 
employees that are under their supervision, in order to aprove or 
reject the corresponding reimbursement budgets. The administrator 
handles the frontend view for handling this functionality, while 
the backend updates the internal database accordingly.

\newpage
\textbf{FBD9. Employee Spending Limit Configuration}

Provide administrative users the ability to set spending limits for 
employees under their supervision. The frontend handles the visual 
logic of this functionality, while the backend registers the new 
employee limit in the database.

\textbf{FBD10. Submitted  and Reviewed Expenses Records Visualization}

Enable users to view their submitted reports record with its 
corresponding current status. Administrator are also able to see 
their reviewed reports record, including their approval or rejection 
decision. To do that, the frontend calls the backend API to retrieve the 
accurate information and displays it to the user through a visual dashboard.

\textbf{FBD11. Email Notification Service Integration}

Send email notifications to the approver when there are new submitted reports pending to review, 
or to the employee when their report is approved or rejected. The backend 
handles all email notifications triggered by frontend actions.
