\subsubsection{Functional Requirements}
These are the functional requirements of the final product:

\begin{itemize}[leftmargin=0.5cm,label={}]

    \item \textbf{FR1:} The application must centralize expenses data in a single platform.

    \item \textbf{FR2:} The application must enable effortless uploads and drag-and-drop of receipts.

    \item \textbf{FR3:} The application must automate the extraction of relevant data from uploaded receipts using an AI model.

    \item \textbf{FR4:} The application must allow users to review and edit the automatically extracted expenses data.

    \item \textbf{FR5:} The application must provide a search bar and filters for uploaded expenses in order to search by name and filter by category.

    \item \textbf{FR6:} The application must allow users to gather multiple expenses in a single report.

    \item \textbf{FR7:} The application must allow users to complete and edit the report information.

    \item \textbf{FR8:} The application must provide a search bar to find reports by name.

    \item \textbf{FR9:} The application must enable simple submission of expenses report to the corresponding approver.

    \item \textbf{FR10:} The application must allow users to login through the company's employee account.

    \item \textbf{FR11:} The application must display a user account page showing the total budget of all submitted reports, categorized as:
        \begin{itemize}
            \item Pending approval or rejection budget
            \item Approved budget
            \item Rejected budget
        \end{itemize}

    \item \textbf{FR12:} The application must send email notifications when a submitted report is approved or rejected.

    \item \textbf{FR13:} The application must implement role-based access control for employees and admins:
        \begin{itemize}[label={}]
            \item \textbf {Employees} can use all previously listed features.
            \item \textbf {Admins} can use all employee features plus the additional features listed below.
        \end{itemize}

    \item \textbf{FR14:} The application must allow admin users to approve or reject submitted expenses reports from employees under their supervision.

    \item \textbf{FR15:} The application must display the history of all reviewed reports (approved or rejected).

    \item \textbf{FR16:} The application must enable admins to set the expenses budget limit for those employees under their supervision.

    \item \textbf{FR17:} The application must send email notifications to users when an employee under their supervision submits an expense report pending approval or rejection.

    \item \textbf{FR18:} The application must provide a monthly summary of the total submitted budget by employees under their supervision.

\end{itemize}