\subsubsection{Non-Functional Requirements}
These are the non-functional requirements of the final product:

\begin{itemize}[leftmargin=0.5cm,label={}]
    \item \textbf {NFR1: The application must provide real-time dashboards for tracking receipt status to improve UX.}
    
    Users should be able to check the current status of their reports submissions.

    \item \textbf {NFR2: The application must offer an interactive, responsive, reactive, and user-friendly UI.}
    
    The UI must be interactive–every user action should trigger a response. The UI must also be responsive, 
    meaning it adapts automatically to any device or screen size. Additionally, the UI must be reactive, this 
    behaviour is needed as the UI and the internal server are two separate components that communicate with 
    each other. Updating the UI without repeatedly calling the server is an important practice to prevent 
    server overloaded\cite{reactive-responsive-interactive}. Finally, the UI should be intuitive and easy to use, a new user should not need 
    more than five minutes to learn how to navigate the app.

    \item \textbf {NFR3: The application must ensure high application performance and availability.}
    
    High performance delivers a fast and smooth user experience. Any action within the application should not take longer than 
    four seconds to complete. The application should also maintain high availability, meaning users can access it 24 hours a day, 
    365 days a year.
    
    \item \textbf {NFR4: The application must support high scalability as the company grows.}
    
    The app should remain stable and responsive even when the number of employees using the app increases significantly.

    \item \textbf {NFR5: The application must guarantee data storage compliance with GDPR.}
    
    FSP is a UK-based company, therefore, the expenses application should also comply with the General Data Protection Regulation(GDPR).

    \item \textbf {NFR6: The application must ensure secure sensitive information storage, as well as secure information access and submission.}
    
    Any sensitive data stored by the web-app should not be leaked. Additionally, the app should also control who can access that information, 
    and also protect it from external parties during the submission.

    \item \textbf {NFR7: The application must enable efficient and intuitive expense management process.}
    
    Employees should find the new expense managing process much faster and easier than the traditional one.

    \item \textbf {NFR8: The application must ensure efficient processing for approval and rejection of expenses reports.}
    
    Approvers should also be able to review and manage submitted expenses more quickly and efficiently.

    \item \textbf {NFR9: The application must provide an integration-friendly architecture.}
    
    Meeting this requirement facilitates the integration of new AI models in the future.

\end{itemize}