\subsection{Monitoring Tools}
The use of monitoring tools makes it easier for the project to follow 
the Agile methodology. Moreover, most of the solutions are essential 
in software development projects, as they help prevent the loss of the 
work if any system or device fails unexpectedly during the development 
process. 
\subsubsection{Git}

A version control system which allows multiple developers to work on 
the same project and enables a single user to develop several features 
at the same time. These capabilities make Git an essential tool for 
software product development. 

In Git, a repository is the location where the application’s source 
code is stored. It serves as a project space where developers submit 
their code, allowing changes to be tracked throughout the development 
process.

\subsubsection{Azure DevOps}

Azure is a cloud resource that offers multiple tools. This project 
makes use of two of them: the Git repository and the backlog dashboard. 

In the backlog, four statuses are assigned to tasks:

\begin {itemize}
\item \textbf{New}: A task that has been defined but it is pending 
development, or a bug that is pending resolution.
\item \textbf{Active}: A task that is currently in development.
\item \textbf{Resolved}: A bug that has been fixed.
\item \textbf{Closed}: A task that has been developed, integrated and tested.
\end{itemize}

\subsubsection{Microsoft Teams}

Communication tool used in FSP. It is used primarily by the Scrum Master 
and the author used primarily for chats and meetings.

\subsubsection{Gmail}

An email platform used for communication between the author and the thesis director.
