\subsection{Market Analysis}

The market already offers millions of available expenses 
management applications. However, in this section only the 
most recognized and competent examples are pointed out. 
Analyzing today's market solutions helps identify market gaps 
while leading the ongoing application to meet industry standards 
and prioritize the most crucial features.

Evidently, the following competent platforms mentioned are assumed 
to include the basic features of a simplified expense management 
process. This includes centralized expense data, digital expense 
management and reporting, streamlined information submissions, and 
secure login access through the company's employee account. 

To delve deeper into the main differences between available potential 
market offerings, consider Table 1, which shows a comparative 
overview of these platforms. Green cells indicate features that the 
application offers, while red cells indicate features that it does not. 
In the last row, the cost of each example is presented in detail.

%Comparative Analysis of Leading Expense Management Solutions (own creation)

\begin{table}[H]
\centering
\small
\renewcommand{\arraystretch}{2}
\begin{tabular}{|p{4cm}|>{\centering\arraybackslash}p{2.2cm}|>{\centering\arraybackslash}p{2.2cm}|>{\centering\arraybackslash}p{2.2cm}|>{\centering\arraybackslash}p{2.2cm}|}
\hline
\cellcolor{orange!45}\textbf{Feature} & \cellcolor{orange!25}\textbf{SAP Concur} & \cellcolor{orange!25}\textbf{Zoho Expense} & \cellcolor{orange!25}\textbf{Expensify} & \cellcolor{orange!25}\textbf{Payhawk} \\ \hline
\cellcolor{orange!25} AI-powered data extraction & \cellcolor{green!25}  & \cellcolor{green!25}  & \cellcolor{green!25}  & \cellcolor{green!25}  \\ \hline
\cellcolor{orange!25} OCR technology & \cellcolor{green!25}  & \cellcolor{green!25}  & \cellcolor{green!25}  & \cellcolor{green!25}  \\ \hline
\cellcolor{orange!25} Intuitive UI & \cellcolor{red!25}  & \cellcolor{green!25}  & \cellcolor{green!25}  & \cellcolor{green!25}  \\ \hline
\cellcolor{orange!25} Limit employee's spending & \cellcolor{red!25}  & \cellcolor{green!25}  & \cellcolor{green!25}  & \cellcolor{green!25}  \\ \hline
\cellcolor{orange!25} Approval processes customized & \cellcolor{red!25}  & \cellcolor{green!25}  & \cellcolor{green!25}  & \cellcolor{green!25}  \\ \hline
\cellcolor{orange!25} Global reimbursements & \cellcolor{red!25}  & \cellcolor{red!25}  & \cellcolor{green!25}  & \cellcolor{green!25} \\ \hline
\cellcolor{orange!25} Virtual cards & \cellcolor{red!25}  & \cellcolor{red!25}  & \cellcolor{green!25}  & \cellcolor{green!25}  \\ \hline
\cellcolor{orange!25} Automated VAT extraction & \cellcolor{red!25}  & \cellcolor{red!25}  & \cellcolor{red!25}  & \cellcolor{green!25}  \\ \hline
\cellcolor{cyan!35} Cost & \cellcolor{cyan!25}High & \cellcolor{cyan!25}Subscription-based & \cellcolor{cyan!25}Cost-per-use & \cellcolor{cyan!25}Subscription-based \\ \hline
\end{tabular}
\caption{Comparative Analysis of Leading Expense Management Solutions (own creation)}
\end{table}
As demonstrated in this table, all options share two common features: 
AI-powered data extraction and OCR technology. Both are indispensable 
for automated expense management. The AI model serves as an automatic 
extraction tool for selecting the relevant information from receipts, 
while the OCR technology automatically converts a text-content image 
into a machine-readable text\cite{ocr-technology}.

In this project, incorporating an AI model is essential to simplify 
expense data extraction. The final product will include this tool, 
as discussed previously in Section 1.1.4. Nevertheless, since it is
only a web-app (not a mobile-app), it is not considered to include
the possibility to allow end-users to upload receipts via a camera, 
integrating OCR technology is unnecessary and so, will not be 
included in the final implementation.

However, going back to Table 1, there are evident differences in 
target markets and secondary features. For instance, SAP Concur 
dominates the large enterprise sector\cite{sap-concur} but is criticized for 
its non-intuitive user interface and high-cost plans \cite{sap-concur-vs-zoho}. In contrast, 
Zoho Expense and Expensify target small businesses with more 
user-friendly interfaces, more affordable pricing, and additional 
features not included in SAP Concur\cite{zoho-expense}\cite{expensify}. The last example introduces 
Payhawk, which includes a new feature that has not been offered by the 
previous platforms yet: automated receipts VAT extraction\cite{payhawk}. 

Despite their strengths, this analysis clearly reveals common areas 
for improvement. An interesting feature for FSP and similar companies 
would be real-time email notifications—such as alerting employees when 
an expense report has been rejected or approved, and notifying approvers 
when a report is submitted and pending review.
